The Emperor Has No Clothes

### 2011-04-01 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5808 ac11df5e-a788-c23b-a8e1-c758c323924d

>>>>

\section{On the Energetics of the LBG Clump Model}
\label{sec:energy}

In the previous section, we demonstrated that the LBG clump model
of S+10 does not reproduce the observed \lya\ emission associated with
LBGs.   We also emphasize, however, that the radiative transfer of
\lya\ is sensitive to the intrinsic emission of the galaxy ($r \sim
10$\,kpc), the physics of the gas in the CGM ($r \sim 100$\,kpc), and
also the property of the IGM on larger scales ($r \sim 1-10$\,Mpc).
It is possible, therefore, that the observed \lya\ emission is
dominated by components other than a galactic-scale wind, indirectly
observed as blue-shifted absorption.  In this respect, the LBG clump
model cannot be ruled out.
